### 2018-01-31 includes/introduction.tex
More renaming.

    \item \textbf{A repository of \smtfull{} instances}:
        We present a repository of \smtfull{} string and regex problem suites
        we generated using \fuzzer{} in section~\ref{sec:suites}. The
        repository consists of two categories: \texttt{generated}, with new
        instances generated by \fuzzer{}, and \texttt{transformed}, with
        transformed instances generated from a small suite of industrial
        benchmarks.

>>>>

    \item \textbf{A repository of \smtfull{} instances}:
        We present a repository of \smtfull{} string and regex instance suites
        we generated using \fuzzer{} in section~\ref{sec:suites}. The
        repository consists of two categories: \texttt{generated}, with new
        instances generated by \fuzzer{}, and \texttt{transformed}, with
        transformed instances generated from a small suite of industrial
        benchmarks.

### 2018-01-31 includes/stringfuzz.tex
More renaming.

\fuzzer{} is implemented as a Python package, and comes with several
executables to generate, transform, and analyze \smtfull{} string and regex
problems. It can either be installed from source, or from the Python
PIP package repository.\footnote{The link to the
source code will be added after double-blind review.}
\fuzzer{} is organized to be easily extended:
all generators and transformers are independent Python modules. Its
components are also implemented as \unix{} ``filters'', to enable easy
integration with other tools (including themselves). For example, the
outputs of generators can be piped into transformers, and transformers
can be chained to produce a stream of tuned inputs to a
solver. \fuzzer{} is composed of the following tools:
\begin{description}
    \item[\generator{}] \hfill \\
        This tool generates \smt{} problems. It supports several generators and
        options that specify its output. Details can be found in
        table~\ref{tbl:generators}.
    \item[\transformer{}] \hfill \\
        This tool transforms \smt{}
        problems. It supports several transformers and options that specify
        its output and input, which are explained in
        table~\ref{tbl:transformers}. Note that transformers
        \textit{Translate} and \textit{Reverse} also preserve
        satisfiability under certain conditions~\cite{ifaz}.
    \item[\texttt{stringstats}] \hfill \\
        This tool takes an \smt{}
        problem as input and outputs its properties: the number of
        variables/literals, the max/median syntactic depth of expressions, the
        max/median literal length, etc.
\end{description}

\begin{table}[t]
    \centering
    \caption{\generator{} generators.}
    \label{tbl:generators}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}        & \textbf{Generated Problems have ...} \\ \hline
        \textit{Concats}     & Long concats and optional random extracts. \\ \hline
        \textit{Lengths}     & Many variables (and their concats) with length constraints. \\ \hline
        \textit{Overlaps}    & An expression of the form A.X = X.B. \\ \hline
        \textit{Equality}    & An equality among concats, each with variables or constants. \\ \hline
        \textit{Regex}       & Regexes of varying complexity. \\ \hline
        \textit{Random-Text} & Random, likely syntactically \textit{in}valid text. \\ \hline
        \textit{Random-AST}  & Random, but semantically \textit{valid} text. \\ \hline
    \end{tabular}
    \caption{\transformer{} transformers.}
    \label{tbl:transformers}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}        & \textbf{The transformer ...} \\ \hline
        \textit{Fuzz}        & Randomly replaces literals and operators with similar ones. \\ \hline
        \textit{Graft}       & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
        \textit{Multiply}    & Multiplies each number by N, and repeats each character N times. \\ \hline
        \textit{Nop}         & Doesn't transform (but can translate \smtfull{}). \\ \hline
        \textit{Reverse}     & Reverses all string literals and concat arguments. \\ \hline
        \textit{Rotate}      & Performs a random syntax tree rotation on two concats. \\ \hline
        \textit{Translate}   & Maps every character X to a different character Y. \\ \hline
        \textit{Unprintable} & Randomly replaces all characters in literals with unprintable ones. \\ \hline
    \end{tabular}
\end{table}

@@

\fuzzer{} can generate
and transform problems with regular expression constraints. The
command \texttt{stringfuzzg regex} invokes the regex problem
generator. It generates a problem of the form:
\begin{align*}
    & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
    & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
    & \texttt{(assert (<= Min (str.len X)))}? \\
    & \texttt{(assert (<= (str.len X)) Max)}?
\end{align*}

where $R_i \in RegEx$, and $Min, Max \in Int$. More simply, the
problem is a set of one or more regex constraints on a single
variable, with optional maximum and minimum length constraints. The
regex constraints $R$ are each of the form:
\begin{align*}
  & \texttt{(re.++}\; \ T_0\; \ T_1\; \texttt{...}\; T_n\; \texttt{)}
\end{align*}

@@

\fuzzer{} can be used to
generate benchmark suites in a batch mode, or can be used in an online
randomized fashion for exploratory debugging. For example, \fuzzer{}
can be invoked as follows to feed random problems to \cvc{} until it
returns an error:
% \vspace{-0.15in}
% \begin{figure}[H]
%     \centering
%     \begin{minipage}[b]{0.91\linewidth}
%         \begin{minted}{bash}
{\scriptsize\begin{verbatim}
while stringfuzzg -r random-ast -m | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
    sleep 0
done\end{verbatim}}
%         \end{minted}
%     \end{minipage}
% \end{figure}
% \vspace{-0.15in}

Some more \unix{} scripting can yield other interesting results. For
example, the following script finds a regex problem on which \us{}
times out after 5 seconds:
% \vspace{-0.15in}
% \begin{figure}[H]
%     \centering
%     \begin{minipage}[b]{0.91\linewidth}
%         \begin{minted}{bash}
{\scriptsize\begin{verbatim}while true; do
    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
    result=`z3str3 -T:5 problem.smt25`
    echo $result
    if [ "$result" == "timeout" ]; then
        cat problem.smt25
        break
    fi
done\end{verbatim}}
%         \end{minted}
%     \end{minipage}
% \end{figure}
% \vspace{-0.15in}

>>>>

\fuzzer{} is implemented as a Python package, and comes with several
executables to generate, transform, and analyze \smtfull{} string and regex
instances. It can either be installed from source, or from the Python
PIP package repository.\footnote{The link to the
source code will be added after double-blind review.}
\fuzzer{} is organized to be easily extended:
all generators and transformers are independent Python modules. Its
components are also implemented as \unix{} ``filters'', to enable easy
integration with other tools (including themselves). For example, the
outputs of generators can be piped into transformers, and transformers
can be chained to produce a stream of tuned inputs to a
solver. \fuzzer{} is composed of the following tools:
\begin{description}
    \item[\generator{}] \hfill \\
        This tool generates \smt{} instances. It supports several generators and
        options that specify its output. Details can be found in
        table~\ref{tbl:generators}.
    \item[\transformer{}] \hfill \\
        This tool transforms \smt{}
        instances. It supports several transformers and options that specify
        its output and input, which are explained in
        table~\ref{tbl:transformers}. Note that transformers
        \textit{Translate} and \textit{Reverse} also preserve
        satisfiability under certain conditions~\cite{ifaz}.
    \item[\texttt{stringstats}] \hfill \\
        This tool takes an \smt{}
        instance as input and outputs its properties: the number of
        variables/literals, the max/median syntactic depth of expressions, the
        max/median literal length, etc.
\end{description}

\begin{table}[t]
    \centering
    \caption{\generator{} generators.}
    \label{tbl:generators}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}        & \textbf{Generated instances have ...} \\ \hline
        \textit{Concats}     & Long concats and optional random extracts. \\ \hline
        \textit{Lengths}     & Many variables (and their concats) with length constraints. \\ \hline
        \textit{Overlaps}    & An expression of the form A.X = X.B. \\ \hline
        \textit{Equality}    & An equality among concats, each with variables or constants. \\ \hline
        \textit{Regex}       & Regexes of varying complexity. \\ \hline
        \textit{Random-Text} & Random, likely syntactically \textit{in}valid text. \\ \hline
        \textit{Random-AST}  & Random, but semantically \textit{valid} text. \\ \hline
    \end{tabular}
    \caption{\transformer{} transformers.}
    \label{tbl:transformers}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}        & \textbf{The transformer ...} \\ \hline
        \textit{Fuzz}        & Randomly replaces literals and operators with similar ones. \\ \hline
        \textit{Graft}       & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
        \textit{Multiply}    & Multiplies each number by N, and repeats each character N times. \\ \hline
        \textit{Nop}         & Doesn't transform (but can translate \smtfull{}). \\ \hline
        \textit{Reverse}     & Reverses all string literals and concat arguments. \\ \hline
        \textit{Rotate}      & Performs a random syntax tree rotation on two concats. \\ \hline
        \textit{Translate}   & Maps every character X to a different character Y. \\ \hline
        \textit{Unprintable} & Randomly replaces all characters in literals with unprintable ones. \\ \hline
    \end{tabular}
\end{table}

@@

\fuzzer{} can generate
and transform instances with regular expression constraints. The
command \texttt{stringfuzzg regex} invokes the regex instance
generator. It generates a instance of the form:
\begin{align*}
    & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
    & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
    & \texttt{(assert (<= Min (str.len X)))}? \\
    & \texttt{(assert (<= (str.len X)) Max)}?
\end{align*}

where $R_i \in RegEx$, and $Min, Max \in Int$. More simply, the
instance is a set of one or more regex constraints on a single
variable, with optional maximum and minimum length constraints. The
regex constraints $R$ are each of the form:
\begin{align*}
  & \texttt{(re.++}\; \ T_0\; \ T_1\; \texttt{...}\; T_n\; \texttt{)}
\end{align*}

@@

\fuzzer{} can be used to
generate benchmark suites in a batch mode, or can be used in an online
randomized fashion for exploratory debugging. For example, \fuzzer{}
can be invoked as follows to feed random instances to \cvc{} until it
returns an error:
% \vspace{-0.15in}
% \begin{figure}[H]
%     \centering
%     \begin{minipage}[b]{0.91\linewidth}
%         \begin{minted}{bash}
{\scriptsize\begin{verbatim}
while stringfuzzg -r random-ast -m | tee instance.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
    sleep 0
done\end{verbatim}}
%         \end{minted}
%     \end{minipage}
% \end{figure}
% \vspace{-0.15in}

Some more \unix{} scripting can yield other interesting results. For
example, the following script finds a regex instance on which \us{}
times out after 5 seconds:
% \vspace{-0.15in}
% \begin{figure}[H]
%     \centering
%     \begin{minipage}[b]{0.91\linewidth}
%         \begin{minted}{bash}
{\scriptsize\begin{verbatim}while true; do
    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > instance.smt25
    result=`z3str3 -T:5 instance.smt25`
    echo $result
    if [ "$result" == "timeout" ]; then
        cat instance.smt25
        break
    fi
done\end{verbatim}}
%         \end{minted}
%     \end{minipage}
% \end{figure}
% \vspace{-0.15in}

### 2018-01-31 includes/suites.tex
Increasing consistency. Renaming problems.tex to suites.tex. Using the word 'instance' instead of the word 'problem'.
More renaming.

\section{Problem Suites}
\label{sec:problems}

@@

Table~\ref{tbl:generated} describes the string and regex instances that were
generated by \generator{}. Table~\ref{tbl:transformed} lists benchmarks
derived from existing seed instances by iteratively applying \transformer{}.
Every transformed instance is named according to its
seed and the transformations it undertook. For example, input
\texttt{z3-regex-1-fuzz-graft.smt2} was transformed by applying
\textit{fuzz} and then \textit{graft} to \texttt{z3-regex-1.smt2}.

@@

\begin{table}[t]
    \centering
    \caption{\generator{}-generated problem sets.}
    \label{tbl:generated}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}             & \textbf{Instances have ...} \\ \hline
        \textit{Concats}          & A single, deep tree of concats. \\ \hline
        \textit{Concats-Extracts} & A single concat tree, and random character extractions. \\ \hline
        \textit{Lengths}          & A single, large length constraint on a variable. \\ \hline
        \textit{Lengths-Concats}  & Variables and their concats, each with fixed lengths. \\ \hline
        \textit{Overlaps}         & A formula of the form A.X = X.B. \\ \hline
        \textit{Regex}            & A test for regex membership of arbitrary complexity. \\ \hline
        \textit{Many-Regexes}     & A test for membership in many random regexes. \\ \hline
        \textit{Regex-Deep}       & A test for membership in a regex with many nested operators. \\ \hline
        \textit{Regex-Pair}       & A test for membership in one regex, but not another. \\ \hline
        \textit{Regex-Lengths}    & A test for membership in a regex, and a length constraint. \\ \hline
    \end{tabular}
\end{table}

\begin{table}[t]
    \centering
    \caption{Transformed problem sets generated by \transformer{}.}
    \label{tbl:transformed}
    \begin{tabular}{|l|l|r|}
        \hline
        \textbf{Name}      & \textbf{Seed}                            & \textbf{Quantity} \\ \hline
        \textit{Amazon}    & Two industrial regex membership problems & 472 \\ \hline
        \textit{Regex}     & Z3str2 regular expression test suite     & 7,551 \\ \hline
        \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples     & 1,170 \\ \hline
    \end{tabular}
\end{table}

>>>>

\section{Instance Suites}
\label{sec:suites}

@@

Table~\ref{tbl:generated} describes the string and regex instances that were
generated by \generator{}. Table~\ref{tbl:transformed} lists benchmarks
derived from existing seed instances by iteratively applying \transformer{}.
Every transformed instance is named according to its
seed and the transformations it undertook. For example, input
\texttt{z3-regex-1-fuzz-graft.smt2} was transformed by applying
\textit{Fuzz} and then \textit{Graft} to \texttt{z3-regex-1.smt2}.

@@

\begin{table}[t]
    \centering
    \caption{\generator{}-generated instances.}
    \label{tbl:generated}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}             & \textbf{Instances have ...} \\ \hline
        \textit{Concats}          & A right-heavy, deep tree of concats. \\ \hline
        \textit{Concats-Balanced} & A balanced, deep tree of concats. \\ \hline
        \textit{Concats-Extracts} & A single concat tree, and random character extractions. \\ \hline
        \textit{Lengths}          & A single, large length constraint on a variable. \\ \hline
        \textit{Lengths-Concats}  & Variables and their concats, each with fixed lengths. \\ \hline
        \textit{Overlaps}         & A formula of the form A.X = X.B. \\ \hline
        \textit{Regex}            & A test for regex membership of arbitrary complexity. \\ \hline
        \textit{Many-Regexes}     & A test for membership in many random regexes. \\ \hline
        \textit{Regex-Deep}       & A test for membership in a regex with many nested operators. \\ \hline
        \textit{Regex-Pair}       & A test for membership in one regex, but not another. \\ \hline
        \textit{Regex-Lengths}    & A test for membership in a regex, and a length constraint. \\ \hline
    \end{tabular}
\end{table}

\begin{table}[t]
    \centering
    \caption{Transformed instances generated by \transformer{}.}
    \label{tbl:transformed}
    \begin{tabular}{|l|l|r|}
        \hline
        \textbf{Name}      & \textbf{Seed}                             & \textbf{Quantity} \\ \hline
        \textit{Amazon}    & Two industrial regex membership instances & 472 \\ \hline
        \textit{Regex}     & Z3str2 regular expression test suite      & 7,551 \\ \hline
        \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples      & 1,170 \\ \hline
    \end{tabular}
\end{table}
